In general, most off-the-shelf solutions are not sufficient since they are not tailored to the process that is used to manage the UTA Summer Conferences. For example, UTASC will handle the systems behind scheduling a camp, using key cards to check in and out of rooms as well as check in and out equipment, handle parking and directly communicate with the UTA parking system, integrating directly into the specific floor plans of the dorm halls at UTA, and managing the various levels of permissions. 
In addition, there are various other specific things that our customer needs UTASC to do that either aren't done in other solutions, don't integrate well with the other systems in UTASC, or are too expensive. In short, our project has merit because we can cheaply provide a very tailored-fit, tightly integrated software solution that covers all our customer's needs, which can't be met with other related works.
The first related work is the Abacre Hotel Management System. It is "a complete hotel management system that begins with taking the guest reservations and check in / check out and ends with billing and tax reports" \cite{website:abacre}. This would only useful for the room check in / check out system. 
The next related work is KWHotel. It is a "hotel management software designed for small and medium accommodation facilities" cite{website:kwhotel}. Again, its functionality is quite limited compared to what we will need to implement for our customer.
Another related work is EZ Rent Out. It is used for renting out equipment, but it has many more features than is needed for our use case. It is also very expensive at \$ 50 per month for the cheapest option and \$ 20 more per additional user cite{website:ezrentout}.
For parking, an existing commercial solution is BOSSCARS. "Tailored to meet the unique needs of colleges and universities, BOSSCARS parking permit software was specifically designed to manage all aspects of parking operations, promote better customer service, and increase revenues" cite{website:bosscars}. This would act as a standalone system, kind of like to replacing UTA's existing system. We just need something that is able to hook into UTA existing parking system and send requests for temporary permits.
Lastly, there is Guest Tracker for room key card management software. "Information including room number, length of stay, and checkout date and time is automatically transferred" to the front desk station cite{website:guesttracker}. This isn't viable since it requires the user to install their custom door handles and use their custom keys while we require a solution that already integrates with their current keycard system. Also, it is very expensive at about \$ 10,000 for enough licenses for the various rooms we are handling.
