To solve the problem, our solution will be divided up into three parts: a database, an API to expose the database, and a frontend to consume the API. The frontend will encompass all parts of the camp process from the beginning contract to the final billing. 

At first, camp coordinators will be able to request UTA to host their camp and if accepted a contract will be sent for them to sign. Basic details will be gathered such as how many bed spaces are needed, dining options, meeting room options, and hall preferences. After these details are finalized, the administration will be able to set the roster, assign campers to rooms, and check them in by giving them a key for their respective room. Parking accommodations would also be logged and sent to UTA Parking at check-in. During a camp’s stay, a camper or camp coordinator is allowed to checkout recreational equipment for billiards, table tennis, etc. which will be logged and tied to a camper’s profile. If at any point a camper loses their card or hard key, a temporary card can be issued and tracked until it is returned either before or at check-out. If during a camper’s stay a room becomes uninhabitable due to a maintenance emergency such as a water leak or bed bug infestation, the system will accommodate a room transfer, allow a work order to be submitted, and finally tracked until the requested action is completed. At check-out, all keys will be tracked and any damages to either the card, card holders, or hard keys including their inability to be returned due to being lost will be logged. After the camp has left, the administration will be able to generate a billing report that will pull information for how many bed spaces were used, how many meeting spaces were needed, number of parking permits submitted, damaged equipment, damaged or lost keys, etc. for a grand total that can also be edited. 

	Various needs will also be met such as creating or editing positions such as a resident assistant, conference assistant, residence director, etc. Their respective permission can be edited at any time to create a hierarchy of access levels. Also, a schedule can be viewed for each hall as to which rooms are being used and at what times.
